### 2021-09-15 paper/localpsf.tex
done working through Tuckers comments

To speed up evaluation of $\convkernel_{x_i}$, we interpolate $\convkernel_{x_i}$ onto a regular rectilinear grid on a coordinate axis aligned box that just barely contains the ellipsoid $E_{x_i}$. We transfer the function $\convkernel_{x_i}$ from the irregular mesh to the regular grid by evaluating $\convkernel_{x_i}$ at all gridpoints in the regular grid, using the slow process described in the previous paragraph. This is an upfront cost which is done ``offline.'' After $\convkernel_{x_i}$ has been transferred to the regular grid, we use fast regular grid interpolation to perform all subsequent ``online'' evaluations of $\convkernel_{x_i}$. This yields a substantial overall speedup because the number of finite element function evaluations required to transfer the functions $\convkernel_{x_i}$ to the regular grid is $O(\fedim)$, while the number of kernel evaluations required to convert $\AopPc$ to H-matrix format is $O(k \fedim \log \fedim)$. Here $\fedim$ is the number of finite element degrees of freedom, and $k$ is the H-matrix rank. Furthermore, transferring $\convkernel_{x_i}$ to a regular grid requires evaluating $\convkernel_{x_i}$ at a predetermined and highly structured collection of points. This structure allows for faster determination of which mesh cells that points are in, and allows one to evaluate the finite element function at all regular gridpoints in parallel. In contrast, constructing the H-matrix requires evaluating $\convkernel_{x_i}$ at an unpredictable sequence of scattered of points, which is an expensive task for finite element function evaluation, but a cheap task for regular grid interpolation. 
Having $\convkernel_{x_i}$ stored on a regular grid also simplifies the implementation of the method that we use to deal with boundary artifacts, which will be described in Section \ref{sec:boundary_extension}.

@@

We convert $\AkerPcMat$ into H1 matrix format using the standard geometrical clustering/adaptive cross method implemented within the HLIBPro software package \cite{HLIBPRO}. Although $\AkerPcMat$ is a dense $\fedim \times \fedim$ matrix, constructing the H-matrix approximation of $\AkerPcMat$ only requires evaluation of $O(\hmatrixrank^2 \fedim \log \fedim)$ entries of $\AkerPc$, and these entries are computed via the formula in Equation \eqref{eq:eval_y_x}. Here $\hmatrixrank$ is the rank of the highest-rank block in the H-matrix. A dense representation of $\AkerPcMat$ is never formed. We describe this H-matrix construction process in detail in Appendix \ref{app:h_matrix}. We convert $\mathbf{M}$ to H-matrix format using standard H-matrix methods for sparse matrices implemented within HLIBPro, using the same recursive block partitioning structure as was used for $\AkerPcMat$.

>>>>

To speed up evaluation of $\convkernel_{x_i}$, we interpolate $\convkernel_{x_i}$ onto a regular rectilinear grid on a coordinate axis aligned box that just barely contains the ellipsoid $E_{x_i}$. We transfer the function $\convkernel_{x_i}$ from the irregular mesh to the regular grid by evaluating $\convkernel_{x_i}$ at all gridpoints in the regular grid, using the slow process described in the previous paragraph. This is an upfront cost which is done ``offline.'' After $\convkernel_{x_i}$ has been transferred to the regular grid, we use fast regular grid interpolation to perform all subsequent ``online'' evaluations of $\convkernel_{x_i}$. This yields a substantial overall speedup because the number of finite element function evaluations required to transfer the functions $\convkernel_{x_i}$ to the regular grid is $O(\fedim)$, while the number of kernel evaluations required to convert $\AopPc$ to H-matrix format is $O(k \fedim \log \fedim)$. Here $\fedim$ is the number of degrees of freedom in the finite element space used to discretize $\combresponse_k$, and $\hmatrixrank$ is the H-matrix rank. Furthermore, transferring $\convkernel_{x_i}$ to a regular grid requires evaluating $\convkernel_{x_i}$ at a predetermined and highly structured collection of points. This structure allows for faster determination of which mesh cell that a point is in, and allows one to evaluate the finite element function at all regular gridpoints in parallel. In contrast, constructing the H-matrix requires evaluating $\convkernel_{x_i}$ at an unpredictable sequence of scattered points, which is an expensive task for finite element function evaluation, but a cheap task for regular grid interpolation. 
Having $\convkernel_{x_i}$ stored on a regular grid also simplifies the implementation of the method that we use to handle boundary artifacts, which will be described in Section \ref{sec:boundary_extension}.

@@

We convert $\AkerPcMat$ into H1 matrix format using the standard geometrical clustering/adaptive cross method implemented within the HLIBpro software package \cite{HLIBPRO}. Although $\AkerPcMat$ is a dense $\fedim \times \fedim$ matrix, constructing the H-matrix approximation of $\AkerPcMat$ only requires evaluation of $O(\hmatrixrank^2 \fedim \log \fedim)$ entries of $\AkerPc$, and these entries are computed via the formula in Equation \eqref{eq:eval_y_x}. Here $\hmatrixrank$ is the rank of the highest-rank block in the H-matrix. A dense representation of $\AkerPcMat$ is never formed. We describe this H-matrix construction process in detail in Appendix \ref{app:h_matrix}. We convert $\mathbf{M}$ to H-matrix format using standard H-matrix methods for sparse matrices implemented within HLIBpro, using the same recursive block partitioning structure as was used for $\AkerPcMat$.
